UCD\\MSc Thesis Proposal:\\\emph{An approach for Continuous Capacity Planning in Cloud Environments with Uptime-based Pricing Model}

### 2015-04-26 paper/paper.tex
abstract

\emph{ /* To be revised. */} \par
\textsl{New Infrastructure as a Service solutions are becoming available with a growing number of supported pricing models. More often than not, a hosted Cloud environment is used to design and build an infrastructure for a product. The recent availability of different pricing schemes based on resource utilization and uptime reveals new challenges in already unpredictable capacity planning process. There is a choice between ad-hoc provisioning and upfront payments with reduced hourly rates. Reserved instances charged upfront are categorized into three groups: light, medium and heavy. Which one is better for a given utilization model? When exactly does one pricing scheme becomes more cost effective? Determining which machine type is better for a given utilization model, or at which point the cost effectiveness of a pricing scheme changes, is vital for the companies subscribing to the IaaS. }

@@

We used modelling and experimentation methodology to build and evaluate the result. The SaaS provider perspective got represented by an availability of per task and per machine metrics. We came up with aggregations and key indicators that helped to characterise an existing state of the configuration. Then, we experimented with algorithms to design ones that can yield positive improvements in the total cost.
Results show proposed approach can achieve a meaningful reduction in the cost by enabling a more optimal assignment of VMs based on uptime and resource utilization.

@@

\section{Input data schema transformation and aggregations}

@@

\begin{enumerate}
\item Capacity growth trend calculation. Update algorithms to suggest optimal configurations using the trend. 
\item Predict price changes and discounts. Moore's Law still works~\cite{7057609} and optimizations that affect future should take this into account.
\item Use horizon charts\footnote{\url{http://vis.berkeley.edu/papers/horizon}} to visualize~\textit{KDI} values. It would be an improvement to the threshold-based report as there might be a set of machines just below the threshold that are not recognized by the report.
\item Research whether~\textit{KDI} correlates to a total cost in bigger sets of data and various pricing environments. If this was true, KDI could be used to validate suggestion algorithms results.

>>>>

\textsl{New Infrastructure as a Service solutions are becoming available with a growing number of supported pricing models. A hosted Cloud environment can be a choice to design and build an infrastructure for a product. The recent availability of different pricing schemes based on resource utilization and uptime reveals new challenges in an already complex capacity planning process. There is a choice between ad-hoc provisioning and time commitment that comes with reduced hourly rates. When one decides for a time commitment, there are still further pricing options available. Few different prices for the same resource that depend on a daily uptime. Which one is the best one? When exactly does one pricing scheme becomes more cost effective that the other? We attempted to answer these critical questions by i) aggregating and transforming metrics data, ii) designing key optimality indicators, iii) using the indicators to build algorithms that suggest better configuration options, iv) using an existing large dataset to evaluate the algorithms. }

@@

We used modelling and experimentation methodology to build and evaluate results. The SaaS provider perspective got represented by an availability of per task and per machine metrics. We came up with aggregations and key indicators that helped to characterise an existing state of the configuration. Then, we experimented with algorithms to design ones that can yield positive improvements in the total cost.
Results show proposed approach can achieve a meaningful reduction in the cost by enabling a more optimal assignment of VMs based on uptime and resource utilization.

@@

\section{Schema transformations and aggregations}

@@

\begin{enumerate}
\item Capacity growth trend calculation. Update algorithms to suggest optimal configurations using the trend. 
\item Predict price changes and discounts. Moore's Law still works~\cite{7057609} and optimizations that affect future should take this into account.
\item Calculate a cost of migration to a newly suggested configuration. This cost should be added to a total cost that is calculated.
\item Use horizon charts\footnote{\url{http://vis.berkeley.edu/papers/horizon}} to visualize~\textit{KDI} values. It would be an improvement to the threshold-based report as there might be a set of machines just below the threshold that are not recognized by the report.
\item Research whether~\textit{KDI} correlates to a total cost in bigger sets of data and various pricing environments. If this was true, KDI could be used to validate suggestion algorithms results.
